---
title: "Covariate Time Series"
---

Purpose: Explore covariate time series data data - trends and step-changes in environmental variables describing climate and dam management.


```{r include=FALSE}
library(tidyverse)
library(zoo)
library(ggpubr)
library(ggside)
library(ggfx)
```


## Load Data Files

Redd count data to get years for rug marks
```{r}
rcdat <- read_csv("Data/Derived/ReddCounts_WGFD_1971-2021_cleaned_withFlowTempCovariates_SeparateFlowComponents_age0.csv") %>% filter(!is.na(reddsperkm)) %>% select(year)
rcsum <- read_csv("ReddCounts_DataSummary.csv")
```

Covariate data
```{r}
jldramp <- read_csv("Data/Derived/JLD_RampDown_Summary_CalendarYear_1960-2022.csv") #%>% rename(broodyr = year)
jldflow <- read_csv("Data/Derived/JLD_ManagedFlow_Covariates_BroodYear_1960-2022.csv")
natflow <- read_csv("Data/Derived/SnakeTribs_NaturalFlow_Covariates_BroodYear_1960-2022.csv") %>% rename(flowstn = site) %>% filter(flowstn %in% c("SnakeBeFlat", "SnakeNat")) 
airtemp <- read_csv("Data/Derived/AirTemperature_Covariates_BroodYear_1960-2022.csv") %>% filter(site %in% c("moose")) %>% rename(tempstn = site)
```

Misc.
```{r}
# color palette
mycols <- c("#E69F00", "#56B4E9", "#009E73", "#999999")

# covariate names
names.covars.new <- c("Duration of ramp down", 
                      "Timing of ramp down", 
                      "Mgd. winter flow variation", 
                      "Mgd. summer mean flow", 
                      "Mgd. peak flow mag. (0)", 
                      "Mgd. peak flow mag. (1)", 
                      "Mgd. peak flow timing", 
                      "Nat. peak flow magnitude", 
                      "Nat. peak flow timing",
                      "Autumn temperature", 
                      "Winter temperature", 
                      "Spring temperature", 
                      "Summer temperature",
                      "Mgd. x Nat. peak flow timing")
```


## Create plots

```{r}
plotlist <- list()
```


### Managed flow

#### Duration of ramp down

Test for change before/after 1989
```{r}
pre <- unlist(jldramp %>% filter(broodyr < 1989) %>% select(jld_rampdur))
post <- unlist(jldramp %>% filter(broodyr >= 1989) %>% select(jld_rampdur))
prepost <- tibble(period = factor(c(rep("pre", times = length(pre)), rep("post", times = length(post))), levels = c("pre", "post")),
                  value = c(unlist(pre), unlist(post)))
t.test(pre, post, alternative = "two.sided")
var.test(pre, post, alternative = "two.sided")
```

Create plot
```{r}
plotlist[[1]] <- eval(substitute(ggplot() +
  geom_point(data = jldramp, mapping = aes(x = broodyr, y = jld_rampdur), shape = 16) +
  geom_line(data = jldramp, mapping = aes(x = broodyr, y = jld_rampdur)) +
  geom_ysideboxplot(data = prepost, mapping = aes(x = period, y = value), orientation = "x", fill = "grey80") +
  xlab("Year") + ylab("Duration of ramp down (days)") +
  geom_rug(data = rcdat, mapping = aes(x = jitter(year, factor = 1.5))) +
  geom_vline(xintercept = 1989, color = "red", linetype = "dashed", linewidth = 0.7) +
  geom_vline(xintercept = 1996, color = "grey50", linetype = "dashed") +
  theme_bw() +
  theme(panel.grid = element_blank(), axis.text = element_text(color = "black"), 
        panel.border = element_rect(color = mycols[1], fill = NA, linewidth = 2),
        ggside.panel.border = element_blank(), ggside.axis.text = element_blank(),
        ggside.axis.ticks = element_blank(), axis.text.y = element_text(angle = 90, hjust = 0.5, vjust = 0.5))))
```

#### Timing of ramp down

Test for change before/after 1989
```{r}
pre <- unlist(jldramp %>% filter(broodyr < 1989) %>% select(jld_rampratemindoy))
post <- unlist(jldramp %>% filter(broodyr >= 1989) %>% select(jld_rampratemindoy))
prepost <- tibble(period = factor(c(rep("pre", times = length(pre)), rep("post", times = length(post))), levels = c("pre", "post")),
                  value = c(unlist(pre), unlist(post)))
t.test(pre, post, alternative = "two.sided")
var.test(pre, post, alternative = "two.sided")
```

Create plot
```{r}
plotlist[[2]] <- eval(substitute(ggplot() +
  geom_point(data = jldramp, mapping = aes(x = broodyr, y = jld_rampratemindoy), shape = 16) +
  geom_line(data = jldramp, mapping = aes(x = broodyr, y = jld_rampratemindoy)) +
  geom_ysideboxplot(data = prepost, mapping = aes(x = period, y = value), orientation = "x", fill = "grey80") +
  xlab("Year") + ylab("Timing of ramp down") +
  geom_rug(data = rcdat, mapping = aes(x = jitter(year, factor = 1.5))) +
  geom_vline(xintercept = 1989, color = "red", linetype = "dashed", linewidth = 0.7) +
  geom_vline(xintercept = 1996, color = "grey50", linetype = "dashed") +
  scale_y_continuous(breaks = c(245, 254, 264, 274, 284), labels = c("1 Sept", "10 Sept", "20 Sept", "30 Sept", "10 Oct")) +
  theme_bw() +
  theme(panel.grid = element_blank(), axis.text = element_text(color = "black"), 
        panel.border = element_rect(color = mycols[1], fill = NA, linewidth = 2),
        ggside.panel.border = element_blank(), ggside.axis.text = element_blank(),
        ggside.axis.ticks = element_blank(), axis.text.y = element_text(angle = 90, hjust = 0.5, vjust = 0.5))))
```


#### Mgd. winter flow variation

Test for change before/after 1989
```{r}
pre <- unlist(jldflow %>% filter(broodyr < 1989) %>% select(jld_winvar))
post <- unlist(jldflow %>% filter(broodyr >= 1989) %>% select(jld_winvar))
prepost <- tibble(period = factor(c(rep("pre", times = length(pre)), rep("post", times = length(post))), levels = c("pre", "post")),
                  value = c(unlist(pre), unlist(post)))
t.test(pre, post, alternative = "two.sided")
var.test(pre, post, alternative = "two.sided")
```

Create plot
```{r}
plotlist[[3]] <- eval(substitute(ggplot() +
  geom_point(data = jldflow, mapping = aes(x = broodyr, y = jld_winvar), shape = 16) +
  geom_line(data = jldflow, mapping = aes(x = broodyr, y = jld_winvar)) +
  geom_ysideboxplot(data = prepost, mapping = aes(x = period, y = value), orientation = "x", fill = "grey80") +
  xlab("Year") + ylab("Mgd. winter flow variation") +
  geom_rug(data = rcdat, mapping = aes(x = jitter(year, factor = 1.5))) +
  geom_vline(xintercept = 1989, color = "red", linetype = "dashed", linewidth = 0.7) +
  geom_vline(xintercept = 1996, color = "grey50", linetype = "dashed") +
  theme_bw() +
  theme(panel.grid = element_blank(), axis.text = element_text(color = "black"), 
        panel.border = element_rect(color = mycols[1], fill = NA, linewidth = 2),
        ggside.panel.border = element_blank(), ggside.axis.text = element_blank(),
        ggside.axis.ticks = element_blank(), axis.text.y = element_text(angle = 90, hjust = 0.5, vjust = 0.5))))
```


#### Mgd. summer mean flow

Test for change before/after 1989
```{r}
pre <- unlist(jldflow %>% filter(broodyr < 1989) %>% select(jld_summean))
post <- unlist(jldflow %>% filter(broodyr >= 1989) %>% select(jld_summean))
prepost <- tibble(period = factor(c(rep("pre", times = length(pre)), rep("post", times = length(post))), levels = c("pre", "post")),
                  value = c(unlist(pre), unlist(post)))
t.test(pre, post, alternative = "two.sided")
var.test(pre, post, alternative = "two.sided")
```

Create plot
```{r}
plotlist[[4]] <- eval(substitute(ggplot() +
  geom_point(data = jldflow, mapping = aes(x = broodyr, y = jld_summean), shape = 16) +
  geom_line(data = jldflow, mapping = aes(x = broodyr, y = jld_summean)) +
  geom_ysideboxplot(data = prepost, mapping = aes(x = period, y = value), orientation = "x", fill = "grey80") +
  xlab("Year") + ylab("Mgd. summer mean flow (cfs)") +
  geom_rug(data = rcdat, mapping = aes(x = jitter(year, factor = 1.5))) +
  geom_vline(xintercept = 1989, color = "red", linetype = "dashed", linewidth = 0.7) +
  geom_vline(xintercept = 1996, color = "grey50", linetype = "dashed") +
  theme_bw() +
  theme(panel.grid = element_blank(), axis.text = element_text(color = "black"), 
        panel.border = element_rect(color = mycols[1], fill = NA, linewidth = 2),
        ggside.panel.border = element_blank(), ggside.axis.text = element_blank(),
        ggside.axis.ticks = element_blank(), axis.text.y = element_text(angle = 90, hjust = 0.5, vjust = 0.5))))
```


#### Mgd. peak flow magnitude

Test for change before/after 1989
```{r}
pre <- unlist(jldflow %>% filter(broodyr < 1989) %>% select(jld_peakmag))
post <- unlist(jldflow %>% filter(broodyr >= 1989) %>% select(jld_peakmag))
prepost <- tibble(period = factor(c(rep("pre", times = length(pre)), rep("post", times = length(post))), levels = c("pre", "post")),
                  value = c(unlist(pre), unlist(post)))
t.test(pre, post, alternative = "two.sided")
var.test(pre, post, alternative = "two.sided")
```

Create plot
```{r}
plotlist[[5]] <- eval(substitute(ggplot() +
  geom_point(data = jldflow, mapping = aes(x = broodyr, y = jld_peakmag), shape = 16) +
  geom_line(data = jldflow, mapping = aes(x = broodyr, y = jld_peakmag)) +
  geom_ysideboxplot(data = prepost, mapping = aes(x = period, y = value), orientation = "x", fill = "grey80") +
  xlab("Year") + ylab("Mgd. peak flow magnitude (cfs)") +
  geom_rug(data = rcdat, mapping = aes(x = jitter(year, factor = 1.5))) +
  geom_vline(xintercept = 1989, color = "red", linetype = "dashed", linewidth = 0.7) +
  geom_vline(xintercept = 1996, color = "grey50", linetype = "dashed") +
  theme_bw() +
  theme(panel.grid = element_blank(), axis.text = element_text(color = "black"), 
        panel.border = element_rect(color = mycols[1], fill = NA, linewidth = 2),
        ggside.panel.border = element_blank(), ggside.axis.text = element_blank(),
        ggside.axis.ticks = element_blank(), axis.text.y = element_text(angle = 90, hjust = 0.5, vjust = 0.5))))
```


#### Mgd. peak flow timing

Test for change before/after 1989
```{r}
pre <- unlist(jldflow %>% filter(broodyr < 1989) %>% select(jld_peaktime))
post <- unlist(jldflow %>% filter(broodyr >= 1989) %>% select(jld_peaktime))
prepost <- tibble(period = factor(c(rep("pre", times = length(pre)), rep("post", times = length(post))), levels = c("pre", "post")),
                  value = c(unlist(pre), unlist(post)))
t.test(pre, post, alternative = "two.sided")
var.test(pre, post, alternative = "two.sided")
```

Create plot
```{r}
plotlist[[6]] <- eval(substitute(ggplot() +
  geom_point(data = jldflow, mapping = aes(x = broodyr, y = jld_peaktime), shape = 16) +
  geom_line(data = jldflow, mapping = aes(x = broodyr, y = jld_peaktime)) +
  geom_ysideboxplot(data = prepost, mapping = aes(x = period, y = value), orientation = "x", fill = "grey80") +
  xlab("Year") + ylab("Mgd. peak flow timing") +
  geom_rug(data = rcdat, mapping = aes(x = jitter(year, factor = 1.5))) +
  geom_vline(xintercept = 1989, color = "red", linetype = "dashed", linewidth = 0.7) +
  geom_vline(xintercept = 1996, color = "grey50", linetype = "dashed") +
  scale_y_continuous(breaks = c(242, 273, 303), labels = c("1 May", "1 June", "1 July")) +
  theme_bw() +
  theme(panel.grid = element_blank(), axis.text = element_text(color = "black"), 
        panel.border = element_rect(color = mycols[1], fill = NA, linewidth = 2),
        ggside.panel.border = element_blank(), ggside.axis.text = element_blank(),
        ggside.axis.ticks = element_blank(), axis.text.y = element_text(angle = 90, hjust = 0.5, vjust = 0.5))))
```


### Nature Flow

#### Nat. peak flow magnitude

Test for linear trend
```{r}
mod <- lm(natq_peakmag ~ broodyr, natflow %>% filter(flowstn == "SnakeNat"))
summary(mod)
```

Create plot
```{r}
plotlist[[7]] <- eval(substitute(ggplot() +
  geom_smooth(data = natflow %>% filter(flowstn == "SnakeNat"), mapping = aes(x = broodyr, y = natq_peakmag), color = mycols[2]) +
  geom_point(data = natflow %>% filter(flowstn == "SnakeNat"), mapping = aes(x = broodyr, y = natq_peakmag), shape = 16) +
  geom_line(data = natflow %>% filter(flowstn == "SnakeNat"), mapping = aes(x = broodyr, y = natq_peakmag)) +
  xlab("Year") + ylab("Nat. peak flow magnitude (cfs)") +
  geom_rug(data = rcdat, mapping = aes(x = jitter(year, factor = 1.5))) +
  xlim(1960,2022) +
  theme_bw() +
  theme(panel.grid = element_blank(), axis.text = element_text(color = "black"), 
        panel.border = element_rect(color = mycols[2], fill = NA, linewidth = 2),
        ggside.panel.border = element_blank(), ggside.axis.text = element_blank(),
        ggside.axis.ticks = element_blank(), axis.text.y = element_text(angle = 90, hjust = 0.5, vjust = 0.5))))
```


#### Nat. peak flow timing

Test for linear trend
```{r}
mod <- lm(natq_peaktime ~ broodyr, natflow %>% filter(flowstn == "SnakeNat"))
summary(mod)
```

Create plot
```{r}
plotlist[[8]] <- eval(substitute(ggplot() +
  geom_smooth(data = natflow %>% filter(flowstn == "SnakeNat"), mapping = aes(x = broodyr, y = natq_peaktime), color = mycols[2]) +
  geom_point(data = natflow %>% filter(flowstn == "SnakeNat"), mapping = aes(x = broodyr, y = natq_peaktime), shape = 16) +
  geom_line(data = natflow %>% filter(flowstn == "SnakeNat"), mapping = aes(x = broodyr, y = natq_peaktime)) +
  xlab("Year") + ylab("Nat. peak flow timing") +
  geom_rug(data = rcdat, mapping = aes(x = jitter(year, factor = 1.5))) +
  scale_y_continuous(breaks = c(256, 273, 287, 303), labels = c("15 May", "1 June", "15 June", "1 July")) +
  xlim(1960,2022) +
  theme_bw() +
  theme(panel.grid = element_blank(), axis.text = element_text(color = "black"), 
        panel.border = element_rect(color = mycols[2], fill = NA, linewidth = 2),
        ggside.panel.border = element_blank(), ggside.axis.text = element_blank(),
        ggside.axis.ticks = element_blank(), axis.text.y = element_text(angle = 90, hjust = 0.5, vjust = 0.5))))
```


### Temperature

#### Autumn temperature

Test for linear trend, entire time series
```{r}
summary(lm(temp_falmean ~ broodyr, airtemp))
```

Since 1980
```{r}
summary(lm(temp_falmean ~ broodyr, airtemp %>% filter(broodyr >= 1980)))
```

Create plot
```{r}
plotlist[[9]] <- eval(substitute(ggplot() +
  geom_smooth(data = airtemp, mapping = aes(x = broodyr, y = temp_falmean), color = mycols[3]) +
  geom_point(data = airtemp, mapping = aes(x = broodyr, y = temp_falmean), shape = 16) +
  geom_line(data = airtemp, mapping = aes(x = broodyr, y = temp_falmean)) +
  xlab("Year") + ylab(expression(paste("Autumn temperature ("^"o", "C)", sep = ""))) +
  geom_rug(data = rcdat, mapping = aes(x = jitter(year, factor = 1.5))) +
  xlim(1960,2022) +
  theme_bw() +
  theme(panel.grid = element_blank(), axis.text = element_text(color = "black"), 
        panel.border = element_rect(color = mycols[3], fill = NA, linewidth = 2),
        ggside.panel.border = element_blank(), ggside.axis.text = element_blank(),
        ggside.axis.ticks = element_blank(), axis.text.y = element_text(angle = 90, hjust = 0.5, vjust = 0.5))))
```


#### Winter temperature

Test for linear trend, entire time series
```{r}
summary(lm(temp_winmean ~ broodyr, airtemp))
```

Since 1980
```{r}
summary(lm(temp_winmean ~ broodyr, airtemp %>% filter(broodyr >= 1980)))
```

Create plot
```{r}
plotlist[[10]] <- eval(substitute(ggplot() +
  geom_smooth(data = airtemp, mapping = aes(x = broodyr, y = temp_winmean), color = mycols[3]) +
  geom_point(data = airtemp, mapping = aes(x = broodyr, y = temp_winmean), shape = 16) +
  geom_line(data = airtemp, mapping = aes(x = broodyr, y = temp_winmean)) +
  xlab("Year") + ylab(expression(paste("Winter temperature ("^"o", "C)", sep = ""))) +
  geom_rug(data = rcdat, mapping = aes(x = jitter(year, factor = 1.5))) +
  xlim(1960,2022) +
  theme_bw() +
  theme(panel.grid = element_blank(), axis.text = element_text(color = "black"), 
        panel.border = element_rect(color = mycols[3], fill = NA, linewidth = 2),
        ggside.panel.border = element_blank(), ggside.axis.text = element_blank(),
        ggside.axis.ticks = element_blank(), axis.text.y = element_text(angle = 90, hjust = 0.5, vjust = 0.5))))
```


#### Spring temperature

Test for linear trend, entire time series
```{r}
summary(lm(temp_sprmean ~ broodyr, airtemp))
```

Since 1980
```{r}
summary(lm(temp_sprmean ~ broodyr, airtemp %>% filter(broodyr >= 1980)))
```

Create plot
```{r}
plotlist[[11]] <- eval(substitute(ggplot() +
  geom_smooth(data = airtemp, mapping = aes(x = broodyr, y = temp_sprmean), color = mycols[3]) +
  geom_point(data = airtemp, mapping = aes(x = broodyr, y = temp_sprmean), shape = 16) +
  geom_line(data = airtemp, mapping = aes(x = broodyr, y = temp_sprmean)) +
  xlab("Year") + ylab(expression(paste("Spring temperature ("^"o", "C)", sep = ""))) +
  geom_rug(data = rcdat, mapping = aes(x = jitter(year, factor = 1.5))) +
  xlim(1960,2022) +
  theme_bw() +
  theme(panel.grid = element_blank(), axis.text = element_text(color = "black"), 
        panel.border = element_rect(color = mycols[3], fill = NA, linewidth = 2),
        ggside.panel.border = element_blank(), ggside.axis.text = element_blank(),
        ggside.axis.ticks = element_blank(), axis.text.y = element_text(angle = 90, hjust = 0.5, vjust = 0.5))))
```


#### Summer temperature

Test for linear trend, entire time series
```{r}
summary(lm(temp_summean ~ broodyr, airtemp))
```

Since 1980
```{r}
summary(lm(temp_summean ~ broodyr, airtemp %>% filter(broodyr >= 1980)))
```

Create plot
```{r}
plotlist[[12]] <- eval(substitute(ggplot() +
  geom_smooth(data = airtemp, mapping = aes(x = broodyr, y = temp_summean), color = mycols[3]) +
  geom_point(data = airtemp, mapping = aes(x = broodyr, y = temp_summean), shape = 16) +
  geom_line(data = airtemp, mapping = aes(x = broodyr, y = temp_summean)) +
  xlab("Year") + ylab(expression(paste("Summer temperature ("^"o", "C)", sep = ""))) +
  geom_rug(data = rcdat, mapping = aes(x = jitter(year, factor = 1.5))) +
  xlim(1960,2022) +
  theme_bw() +
  theme(panel.grid = element_blank(), axis.text = element_text(color = "black"), 
        panel.border = element_rect(color = mycols[3], fill = NA, linewidth = 2),
        ggside.panel.border = element_blank(), ggside.axis.text = element_blank(),
        ggside.axis.ticks = element_blank(), axis.text.y = element_text(angle = 90, hjust = 0.5, vjust = 0.5))))
```


## Combine plots

Combine marginal effects plots for covariates with strong and weak effects only
```{r fig.width=12, fig.height=8}
cp <- egg::ggarrange(plotlist[[1]] + annotation_custom(grid::textGrob("(a)", 0.08, 0.92)) + theme(axis.title.x = element_blank()),
                     plotlist[[2]] + annotation_custom(grid::textGrob("(b)", 0.07, 0.92)) + theme(axis.title.x = element_blank()),
                     plotlist[[3]] + annotation_custom(grid::textGrob("(c)", 0.08, 0.92)) + theme(axis.title.x = element_blank()),
                     plotlist[[4]] + annotation_custom(grid::textGrob("(d)", 0.11, 0.92)) + theme(axis.title.x = element_blank()),
                     plotlist[[5]] + annotation_custom(grid::textGrob("(e)", 0.08, 0.92)) + theme(axis.title.x = element_blank()),
                     plotlist[[6]] + annotation_custom(grid::textGrob("(f)", 0.06, 0.92)) + theme(axis.title.x = element_blank()),
                     plotlist[[7]] + annotation_custom(grid::textGrob("(g)", 0.08, 0.92)) + theme(axis.title.x = element_blank(), plot.margin = unit(c(10, 5.5, 5.5, 5.5), "points")),
                     plotlist[[8]] + annotation_custom(grid::textGrob("(h)", 0.08, 0.92)) + theme(axis.title.x = element_blank()),
                     plotlist[[9]] + annotation_custom(grid::textGrob("(i)", 0.15, 0.92)) + theme(axis.title.x = element_blank()),
                     plotlist[[10]] + annotation_custom(grid::textGrob("(j)", 0.08, 0.92)) + theme(axis.title.x = element_blank()),
                     plotlist[[11]] + annotation_custom(grid::textGrob("(k)", 0.08, 0.92)) + theme(axis.title.x = element_blank()),
                     plotlist[[12]] + annotation_custom(grid::textGrob("(l)", 0.1, 0.92)) + theme(axis.title.x = element_blank()),
                     nrow = 3, ncol = 4, byrow = FALSE, bottom = "Year")

jpeg("Figures/Covariates/Covariates_TimeSeriesData_Combined.jpg", units = "in", width = 12, height = 8, res = 1500)
cp
dev.off()
```
