---
title: "Post-hoc residual analysis"
---


Purpose: explore the relationship between flood duration and residuals from a Ricker model lacking covariates


```{r echo=FALSE}
library(tidyverse)
library(GGally)
library(lubridate)
library(RColorBrewer)
library(R2jags)
library(MCMCvis)
library(loo)
library(HDInterval)
library(scales)
library(data.table)
library(corrplot)
library(ggmcmc)
library(ggeffects)
library(viridis)
library(ggpubr)
# library(mcmcplots)
library(beepr)
library(ggridges)
library(colorblindcheck)
library(DT)
```


## Data

First, use this to pull fish data
```{r}
dat <- read_csv("Data/Derived/ReddCounts_WGFD_1971-2021_cleaned_withFlowTempCovariates_SeparateFlowComponents_age0.csv")
```

Drop Cody (very little data), Salt River tribs, and "ghost years"
```{r}
dat <- dat %>% 
  filter(!stream %in% c("Cody", "Christiansen", "Dave", "Laker")) %>%
  filter(!(stream == "Cowboy Cabin" & year %in% c(1980:1981))) %>%
  filter(!(stream == "Flat" & year %in% c(1976:1979))) %>%
  filter(!(stream == "Spring" & year %in% c(1988:1992)))
```


## Format Fish Data

Log annual redd count data and calculate number of years per population
```{r}
# log 
dat <- dat %>% mutate(rcraw_log = log(reddsperkm))
```

Format fish data into matrices for JAGS model
```{r}
# specify populations
pops <- sort(unique(dat$stream))
n.pops <- length(pops)

# specify years
n.years <- vector(length = n.pops)
years <- matrix(nrow = n.pops, ncol = 51)
for(p in 1:n.pops) {
  n.years[p] <- length(unique(dat$year[dat$stream == pops[p]]))
  years[p,1:n.years[p]] <- sort(unique(dat$year[dat$stream == pops[p]]))
}

# Spawners and Recruits
rec_raw <- matrix(nrow = n.pops, ncol = max(n.years)) 
for(p in 1:n.pops) {
  for(y in 1:n.years[p]) {
    year <- years[p,y]
    rec_raw[p,y] <- dat$rcraw_log[dat$stream == pops[p] & dat$year == year] # Raw, uncorrected ecruits (log scale)
  }#next y
}#next p
```

Get maximum spawners for initialization
```{r}
maxY <- apply(exp(rec_raw), 1, max, na.rm = TRUE)
meanY <- apply(exp(rec_raw), 1, mean, na.rm = TRUE)
```

Check dimensions
```{r}
dim(years)
dim(rec_raw)
```

Add empty columns for model initialization
```{r}
# recruitment
rec_raw <- cbind(matrix(NA, nrow = nrow(rec_raw), ncol = 4), rec_raw)

# years
n.years <- n.years + 4
```

Check dimensions
```{r}
# check dimensions
dim(rec_raw)
max(n.years)
```


## Model in JAGS

### Specify JAGS model

State-space hierarchical Ricker stock-recruitment model with auto-correlated residuals, where observation error is an estimated parameter. No Covariates!
```{r}
cat("model {

##--- LIKELIHOOD ---------------------------------------------------##

# OBSERVATION PROCESS
for (j in 1:numPops) {
    for (i in 1:numYears[j]) {
        logY0[j,i] ~ dnorm(logY[j,i], pow(sigma.oe, -2)) 
        N[j,i] <- exp(logY[j,i])
        }
    }

# STATE PROCESS
for (j in 1:numPops) {

    # STARTING VALUES / INITIALIZATION
    Y1[j] ~ dunif(1, maxY[j])
    Y2[j] ~ dunif(1, maxY[j])
    Y3[j] ~ dunif(1, maxY[j])
    Y4[j] ~ dunif(1, maxY[j])
    logY[j,1] <- log(Y1[j])
    logY[j,2] <- log(Y2[j])
    logY[j,3] <- log(Y3[j])
    logY[j,4] <- log(Y4[j])

    logresid[j,4] <- 0

    # ALL OTHER YEARS
    for (i in 5:numYears[j]) {
        
        # Likelihood and predictions
        logY[j,i] ~ dnorm(logpred2[j,i], pow(sigma.pe[j], -2))
        logpred[j,i] <- logY[j,i-4] + A[j] - B[j] * exp(logY[j,i-4])
        
        # save observations and latent states in loop to exclude starting values from model object
        loglatent[j,i] <- logY[j,i]
        logobserv[j,i] <- logY0[j,i]
        
        # Auto-correlated residuals
        logresid[j,i] <- logY[j,i] - logpred[j,i]
        logpred2[j,i] <- logpred[j,i] + logresid[j,i-1] * phi[j]
        logresid2[j,i] <- logY[j,i] - logpred2[j,i]
        
        # Log-likelihood
        loglik[j,i] <- logdensity.norm(logY0[j,i], logY[j,i], pow(sigma.oe, -2))
        }
    }


##--- PRIORS --------------------------------------------------------##

# Observation error is shared among populations, constrained prior...consider centering this on Baldock et al (2023) CJFAS estimate
sigma.oe ~ dunif(0.001, 100) #dnorm(0, pow(0.5, -2)) T(0,)

# Population-specific parameters
for (j in 1:numPops) {

    # Ricker A
    A[j] ~ dnorm(mu.A, pow(sigma.A, -2)) 

    # Ricker B
    B[j] ~ dnorm(0, pow(1, -2)) T(0,)

    # Process error
    sigma.pe[j] ~ dunif(0.001, 100) #dnorm(0, pow(5, -2)) T(0,)

    # auto-correlated residuals
    phi[j] ~ dunif(-0.99, 0.99)

    }

# Global Ricker A and B
mu.A <- log(exp.mu.A) #dunif(0, 20)
exp.mu.A ~ dunif(0, 20)
sigma.A ~ dunif(0.001, 100)


##--- DERIVED QUANTITIES ---------------------------------------------##

# Population specific carrying capacity
for (j in 1:numPops) { K[j] <- A[j] / B[j] }

}", file = "JAGS Models/Ricker_Hierarchical_StateSpace_OEestimated_NoCovsNull.txt")
```


### Run null model 

Parameters to monitor
```{r}
jags.params <- c("A", "B", "K", "mu.A", "sigma.A", "sigma.oe", "sigma.pe",   # Ricker parameters
                 "logpred", "logpred2",                                      # predictions
                 "loglatent", "logobserv",                                   # latent states and observations
                 "phi", "logresid", "logresid2", "loglik")                   # AR1 term, residuals, log-likelihood
```

Run model in JAGS
```{r eval=FALSE}
st <- Sys.time()
jags.data <- list("logY0" = rec_raw, "numYears" = n.years, "numPops" = n.pops, "maxY" = maxY)
mod_null <- jags.parallel(data = jags.data, inits = NULL, parameters.to.save = jags.params, 
                          model.file = "JAGS Models/Ricker_Hierarchical_StateSpace_OEestimated_NoCovsNull.txt", 
                          n.chains = 20, n.thin = 200, n.burnin = 10000, n.iter = 60000, DIC = TRUE)
MCMCtrace(mod_null, ind = TRUE, params = c("A", "B", "mu.A", "sigma.A", "sigma.oe", "sigma.pe", "mu.coef", "sigma.coef", "p", "phi"),
          filename = "Model output/MCMCtrace_ReddCountsRicker_Test_NoCovs.pdf") # write out traceplots
Sys.time() - st
beep()
```

Save model output as RDS file
```{r eval=FALSE}
saveRDS(mod_null, "Model output/ReddCountsRicker_Phase1_NoCovsNull.RDS")
```

Read in model RDS file
```{r cache=FALSE}
mod_null <- readRDS("Model output/ReddCountsRicker_Phase1_NoCovsNull.RDS")
```

Check R-hat values
```{r}
mod_null$BUGSoutput$summary[,8][mod_null$BUGSoutput$summary[,8] > 1.01]
```


### Set top model

Set top model and save MCMC samples and parameter summary
```{r cache=FALSE}
topmod <- mod_null

# generate MCMC samples and store as an array
modelout <- topmod$BUGSoutput
param.summary <- modelout$summary
McmcList <- vector("list", length = dim(modelout$sims.array)[2])
for(i in 1:length(McmcList)) {
  McmcList[[i]] = as.mcmc(modelout$sims.array[,i,])
}
# rbind MCMC samples from 3 chains 
Mcmcdat <- rbind(McmcList[[1]], McmcList[[2]], McmcList[[3]], McmcList[[4]], McmcList[[5]], 
                 McmcList[[6]], McmcList[[7]], McmcList[[8]], McmcList[[9]], McmcList[[10]], 
                 McmcList[[11]], McmcList[[12]], McmcList[[13]], McmcList[[14]], McmcList[[15]], 
                 McmcList[[16]], McmcList[[17]], McmcList[[18]], McmcList[[19]], McmcList[[20]])
param.summary <- as.data.frame(modelout$summary)
```


## Plot Model Output

### Time series fits

Pull latent and predicted abundance from model output
```{r error=FALSE, message=FALSE, results='hide', warning=FALSE}
# set up matrices: latent states
N_med <- matrix(data = NA, nrow = nrow(rec_raw), ncol = ncol(rec_raw)+4)
N_low <- matrix(data = NA, nrow = nrow(rec_raw), ncol = ncol(rec_raw)+4)
N_upp <- matrix(data = NA, nrow = nrow(rec_raw), ncol = ncol(rec_raw)+4)

# set up matrices: predictions
P_med <- matrix(data = NA, nrow = nrow(rec_raw), ncol = ncol(rec_raw)+4)
P_low <- matrix(data = NA, nrow = nrow(rec_raw), ncol = ncol(rec_raw)+4)
P_upp <- matrix(data = NA, nrow = nrow(rec_raw), ncol = ncol(rec_raw)+4)

# pull latent and predicted abundance from parameter summary
for (j in 1:nrow(rec_raw)) {
  for (i in 1:ncol(rec_raw)+4) {
    loglatent <- NA
    logpred2 <- NA
    
    try(loglatent <- Mcmcdat[,paste("loglatent[",j,",",i,"]", sep = "")])
    try(logpred2 <- Mcmcdat[,paste("logpred2[",j,",",i,"]", sep = "")])
    
    try(N_med[j,i] <- quantile(exp(loglatent), prob = 0.50))
    try(N_low[j,i] <- quantile(exp(loglatent), prob = 0.025))
    try(N_upp[j,i] <- quantile(exp(loglatent), prob = 0.975))
    
    try(P_med[j,i] <- quantile(exp(logpred2), prob = 0.50))
    try(P_low[j,i] <- quantile(exp(logpred2), prob = 0.025))
    try(P_upp[j,i] <- quantile(exp(logpred2), prob = 0.975))
    
  }
}
```

Set up and check color palette for color blindness accessibility
```{r}
rec <- rec_raw
popshort <- c("THCH", "BLKT", "BLCR", "COCA", "FISH", "FLAT", "LTBC", "LOBC", "NOWL", "PRCE", "SRSC", "SPRG", "UPBC")
mycols <- c("orchid1", "forestgreen")# c("darkorange", "dodgerblue") # hcl.colors(2, "Red-Green")
```

Plot time series data with observations, latent states, and model fits.
```{r fig.width=10, fig.height=6.5}
par(mfrow = c(3,5), mgp = c(2,0.6,0), mar = c(1.5, 1.2, 1.5, 1), oma = c(2.5,3,0,0))
for (i in 1:n.pops) {
  plot(exp(rec_raw[i,c(5:55)]) ~ years[i,c(1:51)], type = "n", xlab = "", ylab = "", xlim = c(1970, 2021), ylim = c(0, exp(max(rec_raw[i,], na.rm = T))))
  title(popshort[i], line = 0.25)
  # pop-specific years
  yrpreds <- as.numeric(na.omit(years[i,c(1:51)]))#[1:(length(as.numeric(na.omit(years[i,c(1:51)])))-4)]
  # pop-specific latent states
  nmedpreds <- as.numeric(na.omit(N_med[i,c(5:55)]))
  nlowpreds <- as.numeric(na.omit(N_low[i,c(5:55)]))
  nupppreds <- as.numeric(na.omit(N_upp[i,c(5:55)]))
  # pop-specific predictions
  pmedpreds <- as.numeric(na.omit(P_med[i,c(5:55)]))
  plowpreds <- as.numeric(na.omit(P_low[i,c(5:55)]))
  pupppreds <- as.numeric(na.omit(P_upp[i,c(5:55)]))
  # carrying capacity
  abline(h = param.summary[paste("K[",i,"]", sep = ""),5], lty = 3)
  # plot latent states
  lines(nmedpreds ~ yrpreds, lwd = 1.5, col = mycols[1])
  polygon(x = c(yrpreds, rev(yrpreds)), y = c(c(nlowpreds), rev(nupppreds)), col = scales::alpha(mycols[1], 0.3), border = NA)
  # plot predictions
  lines(pmedpreds ~ yrpreds, lwd = 1.5, col = mycols[2])
  polygon(x = c(yrpreds, rev(yrpreds)), y = c(c(plowpreds), rev(pupppreds)), col = scales::alpha(mycols[2], 0.3), border = NA)
  # plot observations
  points(exp(rec_raw[i,c(5:55)]) ~ years[i,c(1:51)], pch = 1)
  # legend
  #legend("topright", legend = pops[i], bty = "n", border = NA, col = NA, fill = NA, cex = 1.25)
}
mtext("Year", side = 1, line = 1, outer = T, cex = 1.25)
mtext(expression("Redds km"^-1), side = 2, line = 1, outer = T, cex = 1.25)
plot.new()
legend("center", legend = c("Observations", "Latent states", "Predictions"), pch = c(1,NA,NA), lwd = c(NA,2,2), col = c("black", mycols[1], mycols[2]), bty = "n", cex = 1.5)
```


## Residual analysis

```{r}
# get residuals from model 
myrownames <- row.names(param.summary)[grep("logresid2", row.names(param.summary))]
numbers <- str_extract_all(myrownames, "\\d+\\.?\\d*") # Matches integers and decimals
nmstib <- tibble(names = myrownames,
                 popcode = as.numeric(sapply(numbers, "[[", 2)),
                 yearcode = as.numeric(sapply(numbers, "[[", 3))) %>%
  arrange(popcode, yearcode)
# organize into a tibble
residtib <- tibble(stream = dat$stream,
                   year = dat$year,
                   resid = param.summary[nmstib$names,1]) %>%
  mutate(broodyr = year - 4)
# join with flood duration data
flooddur <- read_csv("Data/Derived/FloodDuration.csv") %>% 
  mutate(broodyr = year - 1) 
residtib <- residtib %>% left_join(flooddur %>% select(broodyr, difff, durflood, durflood_raw))
residtib
```

```{r}
residtib %>% ggplot(aes(x = durflood, y = resid)) + geom_point() + geom_smooth()
```

