---
title: "Re-fit model, flood duration"
---


Purpose:


```{r echo=FALSE}
library(tidyverse)
library(GGally)
library(lubridate)
library(RColorBrewer)
library(R2jags)
library(MCMCvis)
library(loo)
library(HDInterval)
library(scales)
library(data.table)
library(corrplot)
library(ggmcmc)
library(ggeffects)
library(viridis)
library(ggpubr)
# library(mcmcplots)
library(beepr)
library(ggridges)
library(colorblindcheck)
library(DT)
```


## Data

First, use this to pull fish data
```{r}
dat <- read_csv("Data/Derived/ReddCounts_WGFD_1971-2021_cleaned_withFlowTempCovariates_SeparateFlowComponents_age0.csv")
```

Pull covariate data for age-0, combine experienced and natural flow datasets
```{r}
dat0 <- read_csv("Data/Derived/ReddCounts_WGFD_1971-2021_cleaned_withFlowTempCovariates_SeparateFlowComponents_age0.csv")
dat0_df <- read_csv("Data/Derived/FloodDuration.csv") %>%
  rename(broodyr = year) %>% 
  mutate(z_durflood = scale(durflood, center = TRUE, scale = TRUE)[,1],
         z_difff = scale(difff, center = TRUE, scale = TRUE)[,1])
dat0 <- dat0 %>% left_join(dat0_df %>% select(broodyr, z_durflood, z_difff))
```

Pull covariate data for age-1, combine experienced and natural flow datasets
```{r}
dat1 <- read_csv("Data/Derived/ReddCounts_WGFD_1971-2021_cleaned_withFlowTempCovariates_SeparateFlowComponents_age1.csv")
dat1_df <- read_csv("Data/Derived/FloodDuration.csv") %>%
  rename(broodyr = year) %>% 
  mutate(broodyr = broodyr + 1,
         z_durflood = scale(durflood, center = TRUE, scale = TRUE)[,1],
         z_difff = scale(difff, center = TRUE, scale = TRUE)[,1])
dat1 <- dat1 %>% left_join(dat1_df %>% select(broodyr, z_durflood, z_difff))
```

Drop Cody (very little data), Salt River tribs, and "ghost years"
```{r}
dat <- dat %>% 
  filter(!stream %in% c("Cody", "Christiansen", "Dave", "Laker")) %>%
  filter(!(stream == "Cowboy Cabin" & year %in% c(1980:1981))) %>%
  filter(!(stream == "Flat" & year %in% c(1976:1979))) %>%
  filter(!(stream == "Spring" & year %in% c(1988:1992)))
```

Create summary table
```{r}
summary.dat <- dat %>% filter(!is.na(reddsperkm)) %>% group_by(stream) %>% summarize('lat' = unique(lat), 'long' = unique(long), 'startyr' = min(year), 'endyr' = max(year), 'n.year' = length(unique(year)), "med.redds" = median(reddsperkm)) %>% arrange(stream) %>% ungroup()
datatable(summary.dat)
# write_csv(summary.dat, "ReddCounts_DataSummary.csv")
```


Plot stock-recruit data
```{r fig.width=8, fig.height=7}
g <- ggplot(dat, aes(x = reddsperkm_lag4, y = reddsperkm, color = broodyr)) +
  theme_bw() +
  geom_smooth(color = "black") +
  geom_point(alpha = 0.75) +
  facet_wrap(~ stream, scales = 'free', ncol = 4) +
  xlab('Spawning redd density (redds/km)') +
  ylab('Recruitment redd density (redds/km)') +
  theme(panel.grid = element_blank())
plot(g)
```
```{r include=FALSE}
jpeg("Figures/ReddCounts/RecruitsBySpawners.jpeg", height = 7, width = 8, units = "in", res = 1000)
plot(g)
dev.off()
```

Plot productivity by stock/spawners
```{r fig.width=8, fig.height=7}
g <- ggplot(dat, aes(x = reddsperkm_lag4, y = log(reddsperkm/reddsperkm_lag4), color = broodyr)) +
  theme_bw() +
  geom_smooth(method ='lm', color = "black") +
  geom_point(alpha = 0.75) +
  facet_wrap(~ stream, scales = 'free', ncol = 4) +
  xlab('Spawning redd density (redds/km)') +
  ylab('ln(Recruits/Spawner)') +
  theme(panel.grid = element_blank())
plot(g)
```
```{r include=FALSE}
jpeg("Figures/ReddCounts/ProductivityBySpawners.jpeg", height = 7, width = 8, units = "in", res = 1000)
g
dev.off()
```

Add misc. variables (currently not used in the model)
```{r eval=FALSE}
# JLD mgmt regime
dat <- dat %>% mutate(regime = ifelse(year < 1989, 0, 1))

# Distance from JLD
djld <- read_csv("Flowline Distance/ReddCount_Sites_JLDDistance.csv") %>%
  filter(!stream %in% c("Dave", "Snake River Side Channel", "Spring"))
```

How much of the variation in productivity is explained by density-dependence alone? (*sensu* Jones *et al.* 2020)
```{r}
dat2 <- dat %>% mutate(lnRS = log(reddsperkm / reddsperkm_lag4), 
                       stream = as_factor(stream))
summary(lm(lnRS ~ reddsperkm_lag4 + stream:reddsperkm_lag4, dat2)) # ~37%
```


## Format Fish Data

Log annual redd count data and calculate number of years per population
```{r}
# log 
dat <- dat %>% mutate(rcraw_log = log(reddsperkm))

# how many years of data does each pop have?
datatable(dat %>% drop_na(rcraw_log) %>% group_by(stream) %>% summarize(nyr = n_distinct(rcraw_log)))
```

Format fish data into matrices for JAGS model
```{r}
# specify populations
pops <- sort(unique(dat$stream))
n.pops <- length(pops)

# specify years
n.years <- vector(length = n.pops)
years <- matrix(nrow = n.pops, ncol = 51)
for(p in 1:n.pops) {
  n.years[p] <- length(unique(dat$year[dat$stream == pops[p]]))
  years[p,1:n.years[p]] <- sort(unique(dat$year[dat$stream == pops[p]]))
}

# Spawners and Recruits
rec_raw <- matrix(nrow = n.pops, ncol = max(n.years)) 
# rec_cor <- matrix(nrow = n.pops, ncol = max(n.years))
# rec_cor_sd <- matrix(nrow = n.pops, ncol = max(n.years))
for(p in 1:n.pops) {
  for(y in 1:n.years[p]) {
    year <- years[p,y]
    rec_raw[p,y] <- dat$rcraw_log[dat$stream == pops[p] & dat$year == year] # Raw, uncorrected ecruits (log scale)
    # rec_cor[p,y] <- dat$rccor_log_mean[dat$stream == pops[p] & dat$year == year] # Corrected recruits (log scale)
    # rec_cor_sd[p,y] <- dat$rccor_log_sd[dat$stream == pops[p] & dat$year == year] # recruitment uncertainty
  }#next y
}#next p
```

Get maximum spawners for initialization
```{r}
maxY <- apply(exp(rec_raw), 1, max, na.rm = TRUE)
meanY <- apply(exp(rec_raw), 1, mean, na.rm = TRUE)
```

Check dimensions
```{r}
dim(years)
dim(rec_raw)
# dim(rec_cor)
# dim(rec_cor_sd)
```


## Format Covariate Data

For age apportionment model (split covariate effects among ages 0 and 1), set up two arrays of covariates: one for covariates lagged to reflect conditions during age-0 (4 years) and another for covariates lagged to reflect conditions during age-1 (3 years)

Get covariate names
```{r}
# names.covars1 <- grep("z", names(dat0), value = TRUE)[c(1:3,5:8,11,14:19)] # age-0
# names.covars0 <- grep("z", names(dat0), value = TRUE)[c(1:3,5:8,14:15,20,16:19)] # age-0
# names.covars0 <- grep("z", names(dat0), value = TRUE)[c(1:3,5:8,20,14:19)] # age-0
names.covars0 <- grep("z", names(dat0), value = TRUE)[c(1:2,6,8:9,16,22,18:21)]#[c(2:3,5,7:9,15:20)] # age-0
# names.covars2 <- grep("z", names(dat1), value = TRUE)[c(1:3,5:8,11,14:19)] # age-1
# names.covars1 <- grep("z", names(dat0), value = TRUE)[c(1:3,5:8,14:15,20,16:19)] # age-1
# names.covars1 <- grep("z", names(dat0), value = TRUE)[c(1:3,5:8,20,14:19)] # age-1
names.covars1 <- grep("z", names(dat1), value = TRUE)[c(1:2,6,8:9,16,22,18:21)]#[c(2:3,5,7:9,15:20)] # age-1

print(names.covars1)
```

Format covariate data into matrices for JAGS model
```{r}
n.covars <- length(names.covars0)
covars0 <- array(data = NA, dim = c(n.pops, max(n.years), n.covars))
covars1 <- array(data = NA, dim = c(n.pops, max(n.years), n.covars))
for(p in 1:n.pops) {
  for(y in 1:n.years[p]) {
    yr <- years[p,y]
    for(c in 1:n.covars) {
      covars0[p,y,c] <- as.numeric(dat0 %>% select(stream, year, names.covars0[c]) %>% filter(stream == pops[p] & year == yr) %>% select(3))
      covars1[p,y,c] <- as.numeric(dat1 %>% select(stream, year, names.covars1[c]) %>% filter(stream == pops[p] & year == yr) %>% select(3))
    } # next c
  } # next y
  #print(p)
} # next p
dim(covars0)
dim(covars1)
```

Add interaction, squared terms, and/or age-specific effects (if applicable).
```{r}
# names.covars0 <- c(names.covars0, "z_int_peaktime", "z_int_peakmag") # add names for additional terms
# names.covars1 <- c(names.covars1, "z_int_peaktime", "z_int_peakmag") # add names for additional terms
# covars0 <- abind::abind(covars0, covars0[,,6]*covars0[,,9], covars0[,,5]*covars0[,,8], along = 3)
# covars1 <- abind::abind(covars1, covars1[,,6]*covars1[,,9], covars1[,,5]*covars1[,,8], along = 3)
# n.covars <- length(names.covars0)

# names.covars0 <- c(names.covars0, "z_int_peakmag", "z_int_peaktime") # add names for additional terms
# names.covars1 <- c(names.covars1, "z_int_peakmag", "z_int_peaktime") # add names for additional terms
# covars0 <- abind::abind(covars0, covars0[,,5]*covars0[,,7], covars0[,,6]*covars0[,,8], along = 3)
# covars1 <- abind::abind(covars1, covars1[,,5]*covars1[,,7], covars0[,,6]*covars0[,,8], along = 3)
# n.covars <- length(names.covars0)

# add terms to covariate name vectors
names.covars0 <- c(names.covars0, "z_jld_peakmag_1", "z_durflood_sqrd") # add names for additional terms
names.covars0[5] <- "z_jld_peakmag_0"
names.covars1 <- c(names.covars1, "z_jld_peakmag_1", "z_durflood_sqrd") # add names for additional terms
names.covars1[5] <- "z_jld_peakmag_0"

# add peak timing interaction and age-1 managed peak magnitude
covars0 <- abind::abind(covars0, covars1[,,5], covars1[,,7]*covars1[,,7], along = 3)
covars1 <- abind::abind(covars1, covars1[,,5], covars1[,,7]*covars1[,,7], along = 3)

# force to age-0 managed flow
covars1[,,5] <- covars0[,,5]

# rearrange order for plotting
names.covars0 <- names.covars0[c(1:5,12,6,7,13,8:11)]
names.covars1 <- names.covars1[c(1:5,12,6,7,13,8:11)]
covars0 <- covars0[,,c(1:5,12,6,7,13,8:11)]
covars1 <- covars1[,,c(1:5,12,6,7,13,8:11)]

# check
n.covars <- length(names.covars0)
```


```{r eval=FALSE}
# OLD - NOT USED
# # set up covariate array
# names.covars <- grep("z", names(dat), value = TRUE)[c(1:8,11,14:19)] # for separated flow components
# names.covars <- grep("z", names(dat), value = TRUE)[c(1:5,7:12)] # for experienced flow
# names.covars <- grep("z", names(dat), value = TRUE)[c(1:3,5:8,11,14:19)]
# names.covars <- grep("z", names(dat), value = TRUE)[c(1:3,14:19)]
# 
# 
# n.covars <- length(names.covars)
# covars <- array(data = NA, dim = c(n.pops, max(n.years), n.covars))
# for(p in 1:n.pops) {
#   for(y in 1:n.years[p]) {
#     yr <- years[p,y]
#     for(c in 1:n.covars) {
#       covars[p,y,c] <- as.numeric(dat %>% select(stream, year, names.covars[c]) %>% filter(stream == pops[p] & year == yr) %>% select(3))
#     } # next c
#   } # next y
#   print(p)
# } # next p
# dim(covars)
# 
# # (for separate flow components) Full interaction model: add array slices for squared terms, interaction terms
# names.covars <- c(names.covars, "z_int_peakmag", "z_int_peaktime", "z_int_winmeanflow", "z_int_jldwinmeanvar") # add names for additional terms
# covars <- abind::abind(covars, covars[,,7]*covars[,,10], covars[,,8]*covars[,,11], covars[,,4]*covars[,,9], covars[,,4]*covars[,,5], along = 3)
# n.covars <- length(names.covars)
# 
# # (for experienced flow) Full interaction model: add array slices for squared terms, interaction terms
# names.covars <- c(names.covars, "z_int_winflowmeanvar", "z_int_peakmagtime") # add names for additional terms
# covars <- abind::abind(covars, covars[,,4]*covars[,,5], covars[,,6]*covars[,,7], along = 3)
# n.covars <- length(names.covars)
# 
# names.covars <- c(names.covars, "z_int_peakmag", "z_int_peaktime", "z_int_winmeanvar") # add names for additional terms
# covars <- abind::abind(covars, covars[,,5]*covars[,,7], covars[,,6]*covars[,,8], covars[,,13]*covars[,,14], along = 3)
# n.covars <- length(names.covars)
# 
# # check dimensions
# dim(covars)
# 
# # create matrix for pre/post 1989
# regime <- matrix(data = NA, nrow = nrow(years), ncol = ncol(years))
# for (i in 1:nrow(regime)) { for (j in 1:ncol(regime)) { regime[i,j] <- ifelse(years[i,j] < 1989, 0, 1) }}
# # names.covars <- c(names.covars, "regime")
# # covars <- abind::abind(covars, regime, along = 3)
# # n.covars <- length(names.covars)

# plot(covars1[,,1] ~ covars2[,,1])
# plot(covars1[,,2] ~ covars2[,,2])
# plot(covars1[,,3] ~ covars2[,,3])
# plot(covars1[,,4] ~ covars2[,,4])
# plot(covars1[,,5] ~ covars2[,,5])
# plot(covars1[,,6] ~ covars2[,,6])
# plot(covars1[,,7] ~ covars2[,,7])
# plot(covars1[,,8] ~ covars2[,,8])
# plot(covars1[,,9] ~ covars2[,,9])
# plot(covars1[,,10] ~ covars2[,,10])
# plot(covars1[,,11] ~ covars2[,,11])
# plot(covars1[,,12] ~ covars2[,,12])
# plot(covars1[,,13] ~ covars2[,,13])
# plot(covars1[,,14] ~ covars2[,,14])
```

Add empty columns for model initialization
```{r}
# recruitment
rec_raw <- cbind(matrix(NA, nrow = nrow(rec_raw), ncol = 4), rec_raw)
# rec_cor <- cbind(matrix(NA, nrow = nrow(rec_cor), ncol = 4), rec_cor)
# rec_cor_sd <- cbind(matrix(NA, nrow = nrow(rec_cor_sd), ncol = 4), rec_cor_sd)

# covariates
# rl <- list()
# for (i in 1:dim(covars)[3]) { rl[[i]] <- cbind(matrix(NA, nrow = nrow(covars), ncol = 4), covars[,,i]) }
# covars <- abind::abind(rl, along = 3)
rl <- list()
for (i in 1:dim(covars0)[3]) { rl[[i]] <- cbind(matrix(NA, nrow = nrow(covars0), ncol = 4), covars0[,,i]) }
covars0 <- abind::abind(rl, along = 3)
rl <- list()
for (i in 1:dim(covars1)[3]) { rl[[i]] <- cbind(matrix(NA, nrow = nrow(covars1), ncol = 4), covars1[,,i]) }
covars1 <- abind::abind(rl, along = 3)

# years
n.years <- n.years + 4

# regime
# regime <- cbind(matrix(NA, nrow = nrow(regime), ncol = 4), regime)
```

Check dimensions
```{r}
# check dimensions
dim(rec_raw)
# dim(rec_cor)
# dim(rec_cor_sd)
# dim(covars)
dim(covars0)
dim(covars1)
max(n.years)
```


## Model in JAGS

### Specify JAGS model

State-space hierarchical Ricker stock-recruitment model with auto-correlated residuals, where observation error is an estimated parameter. Covariates can affect productivity at either age-0 or age-1, with a parameter that estimates the relative importance of effects at each age class. Observations are distributed log-normally around (latent, phases 1-2) redd densities. Log-log scale ensures positive values and allows sigma.oe to be estimated on a log-scale and directly compared to net error model estimates of redd count error from Baldock *et al.* (2023 CJFAS): 0.38 (mean and 95% CI = 0.34, 0.44)
```{r}
cat("model {

##--- LIKELIHOOD ---------------------------------------------------##

# OBSERVATION PROCESS
for (j in 1:numPops) {
    for (i in 1:numYears[j]) {
        logY0[j,i] ~ dnorm(logY[j,i], pow(sigma.oe, -2)) 
        N[j,i] <- exp(logY[j,i])
        }
    }

# STATE PROCESS
for (j in 1:numPops) {

    # STARTING VALUES / INITIALIZATION
    Y1[j] ~ dunif(1, maxY[j])
    Y2[j] ~ dunif(1, maxY[j])
    Y3[j] ~ dunif(1, maxY[j])
    Y4[j] ~ dunif(1, maxY[j])
    logY[j,1] <- log(Y1[j])
    logY[j,2] <- log(Y2[j])
    logY[j,3] <- log(Y3[j])
    logY[j,4] <- log(Y4[j])

    logresid[j,4] <- 0

    # ALL OTHER YEARS
    for (i in 5:numYears[j]) {

        # Derive population and year specific covariate effects 
        for (c in 1:numCovars) { 
            covars0[j,i,c] ~ dnorm(0, pow(1, -2))
            covars1[j,i,c] ~ dnorm(0, pow(1, -2))
            cov.eff[j,i,c] <- coef[j,c] * (((1-p[c]) * covars0[j,i,c]) + (p[c] * covars1[j,i,c])) }
        
        # Likelihood and predictions
        logY[j,i] ~ dnorm(logpred2[j,i], pow(sigma.pe[j], -2))
        logpred[j,i] <- logY[j,i-4] + A[j] - B[j] * exp(logY[j,i-4]) + sum(cov.eff[j,i,1:numCovars])
        
        # save observations and latent states in loop to exclude starting values from model object
        loglatent[j,i] <- logY[j,i]
        logobserv[j,i] <- logY0[j,i]
        
        # Auto-correlated residuals
        logresid[j,i] <- logY[j,i] - logpred[j,i]
        logpred2[j,i] <- logpred[j,i] + logresid[j,i-1] * phi[j]
        logresid2[j,i] <- logY[j,i] - logpred2[j,i]
        
        # Log-likelihood
        loglik[j,i] <- logdensity.norm(logY0[j,i], logY[j,i], pow(sigma.oe, -2))
        }
    }


##--- PRIORS --------------------------------------------------------##

# Observation error is shared among populations, constrained prior...consider centering this on Baldock et al (2023) CJFAS estimate
sigma.oe ~ dunif(0.001, 100) #dnorm(0, pow(0.5, -2)) T(0,)

# Population-specific parameters
for (j in 1:numPops) {

    # Ricker A
    #expA[j] ~ dunif(0, 20)
    #A[j] <- log(expA[j])
    A[j] ~ dnorm(mu.A, pow(sigma.A, -2)) 

    # Ricker B
    B[j] ~ dnorm(0, pow(1, -2)) T(0,)
    #B[j] ~ dnorm(mu.B, pow(sigma.B, -2))

    # Covariate effects
    for (c in 1:numCovars) { coef[j,c] ~ dnorm(mu.coef[c], pow(sigma.coef[c], -2)) }

    # Process error
    sigma.pe[j] ~ dunif(0.001, 100) #dnorm(0, pow(5, -2)) T(0,)

    # auto-correlated residuals
    phi[j] ~ dunif(-0.99, 0.99)

    }

# Global Ricker A and B
mu.A <- log(exp.mu.A) #dunif(0, 20)
exp.mu.A ~ dunif(0, 20)
sigma.A ~ dunif(0.001, 100)
#mu.B ~ dnorm(0, pow(1, -2)) T(0,)
#sigma.B ~ dunif(0.001, 100)

# Global covariate effects
for (c in 1:numCovars) { 
    mu.coef[c] ~ dnorm(0, pow(25, -2)) 
    sigma.coef[c] ~ dunif(0.001, 100) #dnorm(0, pow(5, -2)) T(0.001,100)
    p[c] ~ dunif(0, 1)
    }


##--- DERIVED QUANTITIES ---------------------------------------------##

# Population specific carrying capacity
for (j in 1:numPops) { K[j] <- A[j] / B[j] }

}", file = "JAGS Models/Ricker_Hierarchical_StateSpace_OEestimated_Covars_Proportional.txt")
```


Same as above, but covariates only affect productivity at age-0
```{r}
cat("model {

##--- LIKELIHOOD ---------------------------------------------------##

# OBSERVATION PROCESS
for (j in 1:numPops) {
    for (i in 1:numYears[j]) {
        logY0[j,i] ~ dnorm(logY[j,i], pow(sigma.oe, -2)) 
        N[j,i] <- exp(logY[j,i])
        }
    }

# STATE PROCESS
for (j in 1:numPops) {

    # STARTING VALUES / INITIALIZATION
    Y1[j] ~ dunif(1, maxY[j])
    Y2[j] ~ dunif(1, maxY[j])
    Y3[j] ~ dunif(1, maxY[j])
    Y4[j] ~ dunif(1, maxY[j])
    logY[j,1] <- log(Y1[j])
    logY[j,2] <- log(Y2[j])
    logY[j,3] <- log(Y3[j])
    logY[j,4] <- log(Y4[j])

    logresid[j,4] <- 0

    # ALL OTHER YEARS
    for (i in 5:numYears[j]) {

        # Derive population and year specific covariate effects 
        for (c in 1:numCovars) { 
            covars[j,i,c] ~ dnorm(0, pow(1, -2))
            cov.eff[j,i,c] <- coef[j,c] * covars[j,i,c] }
        
        # Likelihood and predictions
        logY[j,i] ~ dnorm(logpred2[j,i], pow(sigma.pe[j], -2))
        logpred[j,i] <- logY[j,i-4] + A[j] - B[j] * exp(logY[j,i-4]) + sum(cov.eff[j,i,1:numCovars])
                
        # save observations and latent states in loop to exclude starting values from model object
        loglatent[j,i] <- logY[j,i]
        logobserv[j,i] <- logY0[j,i]
        
        # Auto-correlated residuals
        logresid[j,i] <- logY[j,i] - logpred[j,i]
        logpred2[j,i] <- logpred[j,i] + logresid[j,i-1] * phi[j]
        logresid2[j,i] <- logY[j,i] - logpred2[j,i]
        
        # Log-likelihood
        loglik[j,i] <- logdensity.norm(logY0[j,i], logY[j,i], pow(sigma.oe, -2))
        }
    }


##--- PRIORS --------------------------------------------------------##

# Observation error is shared among populations, constrained prior...consider centering this on Baldock et al (2023) CJFAS estimate
sigma.oe ~ dunif(0.001, 100) #dnorm(0, pow(0.5, -2)) T(0,)

# Population-specific parameters
for (j in 1:numPops) {

    # Ricker A
    #expA[j] ~ dunif(0, 20)
    #A[j] <- log(expA[j])
    A[j] ~ dnorm(mu.A, pow(sigma.A, -2)) 

    # Ricker B
    B[j] ~ dnorm(0, pow(1, -2)) T(0,)
    #B[j] ~ dnorm(mu.B, pow(sigma.B, -2))

    # Covariate effects
    for (c in 1:numCovars) { coef[j,c] ~ dnorm(mu.coef[c], pow(sigma.coef[c], -2)) }

    # Process error
    sigma.pe[j] ~ dunif(0.001, 100) #dnorm(0, pow(5, -2)) T(0,)

    # auto-correlated residuals
    phi[j] ~ dunif(-0.99, 0.99)

    }

# Global Ricker A and B
mu.A <- log(exp.mu.A) #dunif(0, 20)
exp.mu.A ~ dunif(0, 20)
sigma.A ~ dunif(0.001, 100)
#mu.B ~ dnorm(0, pow(1, -2)) T(0,)
#sigma.B ~ dunif(0.001, 100)

# Global covariate effects
for (c in 1:numCovars) { 
    mu.coef[c] ~ dnorm(0, pow(25, -2)) 
    sigma.coef[c] ~ dunif(0.001, 100) #dnorm(0, pow(5, -2)) T(0.001,100)
    }


##--- DERIVED QUANTITIES ---------------------------------------------##

# Population specific carrying capacity
for (j in 1:numPops) { K[j] <- A[j] / B[j] }

}", file = "JAGS Models/Ricker_Hierarchical_StateSpace_OEestimated_Covars.txt")
```


### Age-0/1 Proportional

Parameters to monitor
```{r}
jags.params <- c("A", "B", "K", "mu.A", "sigma.A", "sigma.oe", "sigma.pe",   # Ricker parameters
                 "coef", "mu.coef", "sigma.coef", "cov.eff", "p",            # covariate effects
                 "logpred", "logpred2",                                      # predictions
                 "loglatent", "logobserv",                                   # latent states and observations
                 "phi", "logresid", "logresid2", "loglik")                   # AR1 term, residuals, log-likelihood
```

Run model in JAGS
```{r eval=FALSE}
st <- Sys.time()
jags.data <- list("logY0" = rec_raw, "numYears" = n.years, "numPops" = n.pops, "maxY" = maxY, "covars0" = covars0, "covars1" = covars1, "numCovars" = n.covars)
mod_01pb <- jags.parallel(data = jags.data, inits = NULL, parameters.to.save = jags.params, 
                          model.file = "JAGS Models/Ricker_Hierarchical_StateSpace_OEestimated_Covars_Proportional.txt", 
                          n.chains = 20, n.thin = 200, n.burnin = 10000, n.iter = 60000, DIC = TRUE)
MCMCtrace(mod_01pb, ind = TRUE, params = c("A", "B", "mu.A", "sigma.A", "sigma.oe", "sigma.pe", "mu.coef", "sigma.coef", "p", "phi"),
          filename = "Model output/MCMCtrace_ReddCountsRicker_Test_Age01p_winvar_AgeSpecMgdPeakMag_2_TESTFLOODURATION.pdf") # write out traceplots
Sys.time() - st
beep()
```

Save model output as RDS file
```{r eval=FALSE}
saveRDS(mod_01pb, "Model output/ReddCountsRicker_Phase1_Age01p_winvar_AgeSpecMgdPeakMag.RDS")
```

Read in model RDS file
```{r cache=FALSE}
mod_01pb <- readRDS("Model output/ReddCountsRicker_Phase1_Age01p_winvar_AgeSpecMgdPeakMag.RDS")
```

Check R-hat values
```{r}
mod_01pb$BUGSoutput$summary[,8][mod_01pb$BUGSoutput$summary[,8] > 1.01]
```


### Age-0 only

*NOT CURRENTLY USED*

Parameters to monitor
```{r eval=FALSE}
jags.params <- c("A", "B", "K", "mu.A", "sigma.A", "sigma.oe", "sigma.pe",   # Ricker parameters
                 "coef", "mu.coef", "sigma.coef", "cov.eff",            # covariate effects
                 "logpred", "logpred2",                                      # predictions
                 "loglatent", "logobserv",                                   # latent states and observations
                 "phi", "logresid", "logresid2", "loglik")                   # AR1 term, residuals, log-likelihood
```

Run model in JAGS
```{r eval=FALSE}
st <- Sys.time()
jags.data <- list("logY0" = rec_raw, "numYears" = n.years, "numPops" = n.pops, "maxY" = maxY, "covars" = covars0, "numCovars" = n.covars)
mod_0 <- jags.parallel(data = jags.data, inits = NULL, parameters.to.save = jags.params, 
                          model.file = "JAGS Models/Ricker_Hierarchical_StateSpace_OEestimated_Covars.txt", 
                          n.chains = 20, n.thin = 200, n.burnin = 10000, n.iter = 40000, DIC = TRUE)
MCMCtrace(mod_0, ind = TRUE, params = c("A", "B", "mu.A", "sigma.A", "sigma.oe", "sigma.pe", "mu.coef", "sigma.coef", "p", "phi"),
          filename = "Model output/MCMCtrace_ReddCountsRicker_Test_Age0.pdf") # write out traceplots
Sys.time() - st
beep()
```

Check R-hat values
```{r eval=FALSE}
mod_0$BUGSoutput$summary[,8][mod_0$BUGSoutput$summary[,8] > 1.05]
```

Save model output as RDS file
```{r eval=FALSE}
saveRDS(mod_0, "Model output/ReddCountsRicker_Phase1_Age0.RDS")
```

Read in model RDS file
```{r eval=FALSE}
mod_0 <- readRDS("Model output/ReddCountsRicker_Phase1_Age0.RDS")
```


### LOO-CV

```{r cache=FALSE}
ll.arr <- mod_01pb$BUGSoutput$sims.list$loglik # extract the log-likelihood estimates for each MCMC sample
ll.mat <- ll.arr[,,1]
for (j in 2:dim(ll.arr)[3]) {
  ll.mat <- cbind(ll.mat, ll.arr[,,j])
}
rf <- relative_eff(exp(ll.mat), chain_id = rep(1:20, each = 250))
my_loo <- loo(ll.mat, r_eff = rf)
plot(my_loo)
```


### Set top model

Set top model and save MCMC samples and parameter summary
```{r cache=FALSE}
topmod <- mod_01pb

# generate MCMC samples and store as an array
modelout <- topmod$BUGSoutput
param.summary <- modelout$summary
McmcList <- vector("list", length = dim(modelout$sims.array)[2])
for(i in 1:length(McmcList)) {
  McmcList[[i]] = as.mcmc(modelout$sims.array[,i,])
}
# rbind MCMC samples from 3 chains 
Mcmcdat <- rbind(McmcList[[1]], McmcList[[2]], McmcList[[3]], McmcList[[4]], McmcList[[5]], 
                 McmcList[[6]], McmcList[[7]], McmcList[[8]], McmcList[[9]], McmcList[[10]], 
                 McmcList[[11]], McmcList[[12]], McmcList[[13]], McmcList[[14]], McmcList[[15]], 
                 McmcList[[16]], McmcList[[17]], McmcList[[18]], McmcList[[19]], McmcList[[20]])
param.summary <- as.data.frame(modelout$summary)

# save model output
write_csv(as.data.frame(Mcmcdat), "Model output/ReddCountsRicker_Phase1_Age01p_mcmcsamps.csv")
write.csv(as.data.frame(modelout$summary), "Model output/ReddCountsRicker_Phase1_Age01p_ParameterSummary.csv", row.names = T)
```


## Model Diagnostics

Get expected and observed MCMC samples
```{r}
ppdat_exp <- as.matrix(Mcmcdat[,startsWith(colnames(Mcmcdat), "logpred2")])
ppdat_obs <- as.matrix(Mcmcdat[,startsWith(colnames(Mcmcdat), "loglatent")])
```


### Residuals

Histogram of residuals
```{r}
par(mar = c(4,4,1,1), mgp = c(2.5,1,0))
hist((ppdat_obs - ppdat_exp), main = "", xlab = "Observed - Expected")
legend("topright", bty = "n", legend = paste("Median Resid. = ", round(median((ppdat_obs - ppdat_exp)), digits = 4), sep = ""))
abline(v = median(unlist(ppdat_obs - ppdat_exp)), col = "red", lwd = 2)
box(bty = "o")
```

```{r include=FALSE}
jpeg("Figures/Model Diagnostics/ReddCounts_Ricker_CovarModel_Age01_ResidHist.jpg", units = "in", width = 4.5, height = 4.5, res = 1500)
par(mar = c(4,4,1,1), mgp = c(2.5,1,0))
hist((ppdat_obs - ppdat_exp), main = "", xlab = "Residual (observed - expected)")
legend("topright", bty = "n", legend = paste("Median residual \n= ", round(median((ppdat_obs - ppdat_exp)), digits = 4), sep = ""))
abline(v = median(unlist(ppdat_obs - ppdat_exp)), col = "red", lwd = 2)
box(bty = "o")
dev.off()
```


#### Before autocorrelation
```{r}
logresid <- matrix(data = NA, nrow = nrow(rec_raw), ncol = ncol(rec_raw)+4)
for (j in 1:nrow(rec_raw)) {
  for (i in 1:ncol(rec_raw)+4) {
    try(logresid[j,i] <- param.summary[paste("logresid[",j,",",i,"]", sep = ""),1])
  }
}
```

Time series of residuals (AR1)
```{r fig.width=8, fig.height=8}
par(mfrow = c(4,4), mgp = c(2,0.8,0), mar = c(2.5, 3, 1.5, 0.5))
for (i in 1:n.pops) {
  plot(logresid[i,c(5:55)] ~ years[i,c(1:51)], pch = 16, xlab = "", ylab = "log residuals", main = pops[i], xlim = c(1970, 2021), ylim = c(min(logresid, na.rm = T), max(logresid, na.rm = T)))
  lines(logresid[i,c(5:55)] ~ years[i,c(1:51)])
  abline(h = 0, lty = 2)
}
```

```{r include=FALSE}
jpeg("Figures/Model Diagnostics/ReddCounts_Ricker_CovarModel_Age01_Residuals_NoAutocorr_commonscale.jpg", units = "in", width = 8, height = 8, res = 1000)
par(mfrow = c(4,4), mgp = c(2,0.8,0), mar = c(2.5, 3, 1.5, 0.5))
for (i in 1:n.pops) {
  plot(logresid[i,c(5:55)] ~ years[i,c(1:51)], pch = 16, xlab = "", ylab = "log residuals", main = pops[i], xlim = c(1970, 2021), ylim = c(min(logresid, na.rm = T), max(logresid, na.rm = T)))
  lines(logresid[i,c(5:55)] ~ years[i,c(1:51)])
  abline(h = 0, lty = 2)
}
dev.off()
```

time series of residuals (AR1), unique y scale
```{r fig.width=8, fig.height=8}
par(mfrow = c(4,4), mgp = c(2,0.8,0), mar = c(2.5, 3, 1.5, 0.5))
for (i in 1:n.pops) {
  plot(logresid[i,c(5:55)] ~ years[i,c(1:51)], pch = 16, xlab = "", ylab = "log residuals", main = pops[i], xlim = c(1970, 2021))
  lines(logresid[i,c(5:55)] ~ years[i,c(1:51)])
  abline(h = 0, lty = 2)
}
```

```{r include=FALSE}
jpeg("Figures/Model Diagnostics/ReddCounts_Ricker_CovarModel_Age01_Residuals_NoAutocorr_uniquescale.jpg", units = "in", width = 8, height = 8, res = 1000)
par(mfrow = c(4,4), mgp = c(2,0.8,0), mar = c(2.5, 3, 1.5, 0.5))
for (i in 1:n.pops) {
  plot(logresid[i,c(5:55)] ~ years[i,c(1:51)], pch = 16, xlab = "", ylab = "log residuals", main = pops[i], xlim = c(1970, 2021))
  lines(logresid[i,c(5:55)] ~ years[i,c(1:51)])
  abline(h = 0, lty = 2)
}
dev.off()
```


#### After autocorrelation

Residuals AFTER accounting for autocorrelation sensu Murdoch et al 2024 CJFAS
```{r}
logresid <- matrix(data = NA, nrow = nrow(rec_raw), ncol = ncol(rec_raw)+4)
for (j in 1:nrow(rec_raw)) {
  for (i in 1:ncol(rec_raw)+4) {
    try(logresid[j,i] <- param.summary[paste("logresid2[",j,",",i,"]", sep = ""),1])
  }
}
```

time series of residuals (AR1)
```{r fig.width=8, fig.height=8}
par(mfrow = c(4,4), mgp = c(2,0.8,0), mar = c(2.5, 3, 1.5, 0.5))
for (i in 1:n.pops) {
  plot(logresid[i,c(5:55)] ~ years[i,c(1:51)], pch = 16, xlab = "", ylab = "log residuals", main = pops[i], xlim = c(1970, 2021), ylim = c(min(logresid, na.rm = T), max(logresid, na.rm = T)))
  lines(logresid[i,c(5:55)] ~ years[i,c(1:51)])
  abline(h = 0, lty = 2)
}
```

```{r include = FALSE}
jpeg("Figures/Model Diagnostics/ReddCounts_Ricker_CovarModel_Age01_Residuals_wAutocorr_commonscale.jpg", units = "in", width = 8, height = 8, res = 1000)
par(mfrow = c(4,4), mgp = c(2,0.8,0), mar = c(2.5, 3, 1.5, 0.5))
for (i in 1:n.pops) {
  plot(logresid[i,c(5:55)] ~ years[i,c(1:51)], pch = 16, xlab = "", ylab = "log residuals", main = pops[i], xlim = c(1970, 2021), ylim = c(min(logresid, na.rm = T), max(logresid, na.rm = T)))
  lines(logresid[i,c(5:55)] ~ years[i,c(1:51)])
  abline(h = 0, lty = 2)
}
dev.off()
```


time series of residuals (AR1), unique y scale
```{r fig.width=8, fig.height=8}
par(mfrow = c(4,4), mgp = c(2,0.8,0), mar = c(2.5, 3, 1.5, 0.5))
for (i in 1:n.pops) {
  plot(logresid[i,c(5:55)] ~ years[i,c(1:51)], pch = 16, xlab = "", ylab = "log residuals", main = pops[i], xlim = c(1970, 2021))
  lines(logresid[i,c(5:55)] ~ years[i,c(1:51)])
  abline(h = 0, lty = 2)
}
```

```{r include=FALSE}
jpeg("Figures/Model Diagnostics/ReddCounts_Ricker_CovarModel_Age01_Residuals_wAutocorr_uniquescale.jpg", units = "in", width = 8, height = 8, res = 1000)
par(mfrow = c(4,4), mgp = c(2,0.8,0), mar = c(2.5, 3, 1.5, 0.5))
for (i in 1:n.pops) {
  plot(logresid[i,c(5:55)] ~ years[i,c(1:51)], pch = 16, xlab = "", ylab = "log residuals", main = pops[i], xlim = c(1970, 2021))
  lines(logresid[i,c(5:55)] ~ years[i,c(1:51)])
  abline(h = 0, lty = 2)
}
dev.off()
```

Show residual autocorrelation plots by population
```{r fig.width=8, fig.height=8}
par(mfrow = c(4,4), mgp = c(2,0.8,0), mar = c(3, 3, 0.5, 0.5))
for (i in 1:n.pops) {
  pacf(logresid[i,][complete.cases(logresid[i,])], main = pops[i])
}
```

### Bayesian p-value

```{r}
# Bayesian p-value
sum(ppdat_exp > ppdat_obs) / (dim(ppdat_obs)[1]*dim(ppdat_obs)[2])
```

### PP Check

Note that this isn't a posterior predictive check in the true sense, but rather a comparison between the model-estimated latent states (log redd density) and the model predicted means. 

```{r}
par(mar = c(4,4,1,1), mgp = c(2.5,1,0))
plot(x = seq(from = 1.5, to = 6.5, length.out = 100), y = seq(from = 1.5, to = 6.5, length.out = 100), pch = NA, xlab = "Latent ln(recruitment)", ylab = "Median posterior expected ln(recruitment)")
points(apply(ppdat_exp, 2, median, na.rm = T) ~ apply(ppdat_obs, 2, median, na.rm = T))
legend("topleft", bty = "n", legend = paste("Bayesian p-value = ", round(sum(ppdat_exp > ppdat_obs) / (dim(ppdat_obs)[1]*dim(ppdat_obs)[2]), digits = 3), sep = ""))
abline(a = 0, b = 1, col = "red", lwd = 2)
```

```{r include=FALSE}
# Posterior Predictive Check: plot median posterior expected length ~ observed length with Bayesian p-value
jpeg("Figures/Model Diagnostics/ReddCounts_Ricker_CovarModel_Age01_PPCheck.jpg", units = "in", width = 4.5, height = 4.5, res = 1500)
par(mar = c(4,4,1,1), mgp = c(2.5,1,0))
plot(x = seq(from = 1.5, to = 6.5, length.out = 100), y = seq(from = 1.5, to = 6.5, length.out = 100), pch = NA, xlab = "Latent ln(recruitment)", ylab = "Median posterior expected ln(recruitment)")
points(apply(ppdat_exp, 2, median, na.rm = T) ~ apply(ppdat_obs, 2, median, na.rm = T))
legend("topleft", bty = "n", legend = paste("Bayesian p-value = ", round(sum(ppdat_exp > ppdat_obs) / (dim(ppdat_obs)[1]*dim(ppdat_obs)[2]), digits = 3), sep = ""))
abline(a = 0, b = 1, col = "red", lwd = 2)
dev.off()
```


## Plot Model Output

### Time series fits

Pull latent and predicted abundance from model output
```{r error=FALSE, message=FALSE, results='hide', warning=FALSE}
# set up matrices: latent states
N_med <- matrix(data = NA, nrow = nrow(rec_raw), ncol = ncol(rec_raw)+4)
N_low <- matrix(data = NA, nrow = nrow(rec_raw), ncol = ncol(rec_raw)+4)
N_upp <- matrix(data = NA, nrow = nrow(rec_raw), ncol = ncol(rec_raw)+4)

# set up matrices: predictions
P_med <- matrix(data = NA, nrow = nrow(rec_raw), ncol = ncol(rec_raw)+4)
P_low <- matrix(data = NA, nrow = nrow(rec_raw), ncol = ncol(rec_raw)+4)
P_upp <- matrix(data = NA, nrow = nrow(rec_raw), ncol = ncol(rec_raw)+4)

# pull latent and predicted abundance from parameter summary
for (j in 1:nrow(rec_raw)) {
  for (i in 1:ncol(rec_raw)+4) {
    # try(N_med[j,i] <- exp(param.summary[paste("loglatent[",j,",",i,"]", sep = ""),5]))
    # try(N_low[j,i] <- exp(param.summary[paste("loglatent[",j,",",i,"]", sep = ""),3]))
    # try(N_upp[j,i] <- exp(param.summary[paste("loglatent[",j,",",i,"]", sep = ""),7]))
    # 
    # try(P_med[j,i] <- exp(param.summary[paste("logpred2[",j,",",i,"]", sep = ""),5]))
    # try(P_low[j,i] <- exp(param.summary[paste("logpred2[",j,",",i,"]", sep = ""),3]))
    # try(P_upp[j,i] <- exp(param.summary[paste("logpred2[",j,",",i,"]", sep = ""),7]))

    loglatent <- NA
    logpred2 <- NA
    
    try(loglatent <- Mcmcdat[,paste("loglatent[",j,",",i,"]", sep = "")])
    try(logpred2 <- Mcmcdat[,paste("logpred2[",j,",",i,"]", sep = "")])
    
    try(N_med[j,i] <- quantile(exp(loglatent), prob = 0.50))
    try(N_low[j,i] <- quantile(exp(loglatent), prob = 0.025))
    try(N_upp[j,i] <- quantile(exp(loglatent), prob = 0.975))
    
    try(P_med[j,i] <- quantile(exp(logpred2), prob = 0.50))
    try(P_low[j,i] <- quantile(exp(logpred2), prob = 0.025))
    try(P_upp[j,i] <- quantile(exp(logpred2), prob = 0.975))
    
  }
}
```

Set up and check color palette for color blindness accessibility
```{r}
rec <- rec_raw
popshort <- c("THCH", "BLKT", "BLCR", "COCA", "FISH", "FLAT", "LTBC", "LOBC", "NOWL", "PRCE", "SRSC", "SPRG", "UPBC")
mycols <- c("orchid1", "forestgreen")# c("darkorange", "dodgerblue") # hcl.colors(2, "Red-Green")
palette_check(col2hcl(mycols), plot = TRUE)
```

Plot time series data with observations, latent states, and model fits.
```{r fig.width=10, fig.height=6.5}
par(mfrow = c(3,5), mgp = c(2,0.6,0), mar = c(1.5, 1.2, 1.5, 1), oma = c(2.5,3,0,0))
for (i in 1:n.pops) {
  plot(exp(rec_raw[i,c(5:55)]) ~ years[i,c(1:51)], type = "n", xlab = "", ylab = "", xlim = c(1970, 2021), ylim = c(0, exp(max(rec_raw[i,], na.rm = T))))
  title(popshort[i], line = 0.25)
  # pop-specific years
  yrpreds <- as.numeric(na.omit(years[i,c(1:51)]))#[1:(length(as.numeric(na.omit(years[i,c(1:51)])))-4)]
  # pop-specific latent states
  nmedpreds <- as.numeric(na.omit(N_med[i,c(5:55)]))
  nlowpreds <- as.numeric(na.omit(N_low[i,c(5:55)]))
  nupppreds <- as.numeric(na.omit(N_upp[i,c(5:55)]))
  # pop-specific predictions
  pmedpreds <- as.numeric(na.omit(P_med[i,c(5:55)]))
  plowpreds <- as.numeric(na.omit(P_low[i,c(5:55)]))
  pupppreds <- as.numeric(na.omit(P_upp[i,c(5:55)]))
  # carrying capacity
  abline(h = param.summary[paste("K[",i,"]", sep = ""),5], lty = 3)
  # plot latent states
  lines(nmedpreds ~ yrpreds, lwd = 1.5, col = mycols[1])
  polygon(x = c(yrpreds, rev(yrpreds)), y = c(c(nlowpreds), rev(nupppreds)), col = scales::alpha(mycols[1], 0.3), border = NA)
  # plot predictions
  lines(pmedpreds ~ yrpreds, lwd = 1.5, col = mycols[2])
  polygon(x = c(yrpreds, rev(yrpreds)), y = c(c(plowpreds), rev(pupppreds)), col = scales::alpha(mycols[2], 0.3), border = NA)
  # plot observations
  points(exp(rec_raw[i,c(5:55)]) ~ years[i,c(1:51)], pch = 1)
  # legend
  #legend("topright", legend = pops[i], bty = "n", border = NA, col = NA, fill = NA, cex = 1.25)
}
mtext("Year", side = 1, line = 1, outer = T, cex = 1.25)
mtext(expression("Redds km"^-1), side = 2, line = 1, outer = T, cex = 1.25)
plot.new()
legend("center", legend = c("Observations", "Latent states", "Predictions"), pch = c(1,NA,NA), lwd = c(NA,2,2), col = c("black", mycols[1], mycols[2]), bty = "n", cex = 1.5)
```

```{r include = FALSE}
jpeg("Figures/Time Series/ReddCountsRicker_Covars_Age01p_TimeSeries_Proportional_95ci.jpg", units = "in", width = 10, height = 6.5, res = 1000)
par(mfrow = c(3,5), mgp = c(2,0.6,0), mar = c(1.5, 1.2, 1.5, 1), oma = c(2.5,3,0,0))
for (i in 1:n.pops) {
  plot(exp(rec_raw[i,c(5:55)]) ~ years[i,c(1:51)], type = "n", xlab = "", ylab = "", xlim = c(1970, 2021), ylim = c(0, exp(max(rec_raw[i,], na.rm = T))))
  title(popshort[i], line = 0.25)
  # pop-specific years
  yrpreds <- as.numeric(na.omit(years[i,c(1:51)]))#[1:(length(as.numeric(na.omit(years[i,c(1:51)])))-4)]
  # pop-specific latent states
  nmedpreds <- as.numeric(na.omit(N_med[i,c(5:55)]))
  nlowpreds <- as.numeric(na.omit(N_low[i,c(5:55)]))
  nupppreds <- as.numeric(na.omit(N_upp[i,c(5:55)]))
  # pop-specific predictions
  pmedpreds <- as.numeric(na.omit(P_med[i,c(5:55)]))
  plowpreds <- as.numeric(na.omit(P_low[i,c(5:55)]))
  pupppreds <- as.numeric(na.omit(P_upp[i,c(5:55)]))
  # carrying capacity
  abline(h = param.summary[paste("K[",i,"]", sep = ""),5], lty = 3)
  # plot latent states
  lines(nmedpreds ~ yrpreds, lwd = 1.5, col = mycols[1])
  polygon(x = c(yrpreds, rev(yrpreds)), y = c(c(nlowpreds), rev(nupppreds)), col = scales::alpha(mycols[1], 0.3), border = NA)
  # plot predictions
  lines(pmedpreds ~ yrpreds, lwd = 1.5, col = mycols[2])
  polygon(x = c(yrpreds, rev(yrpreds)), y = c(c(plowpreds), rev(pupppreds)), col = scales::alpha(mycols[2], 0.3), border = NA)
  # plot observations
  points(exp(rec_raw[i,c(5:55)]) ~ years[i,c(1:51)], pch = 1)
  # legend
  #legend("topright", legend = pops[i], bty = "n", border = NA, col = NA, fill = NA, cex = 1.25)
}
mtext("Year", side = 1, line = 1, outer = T, cex = 1.25)
mtext(expression("Redds km"^-1), side = 2, line = 1, outer = T, cex = 1.25)
plot.new()
legend("center", legend = c("Observations", "Latent states", "Predictions"), pch = c(1,NA,NA), lwd = c(NA,2,2), col = c("black", mycols[1], mycols[2]), bty = "n", cex = 1.5)
dev.off()
```


Population summaries of latent states and carrying capacity, arranged from least to most variable (based on CV).
```{r}
means <- apply(N_med, 1, mean, na.rm = T)
sds <- apply(N_med, 1, sd, na.rm = T)
cvs <- sds/means
mins <- apply(N_med, 1, min, na.rm = T)
maxs <- apply(N_med, 1, max, na.rm = T)
relc <- maxs/mins
ks <- param.summary[grep("K", row.names(param.summary), value = TRUE),5]

poptib <- tibble(pop = pops, mean = round(means, digits = 3), sd = round(sds, digits = 3), cv = round(cvs, digits = 3), min = round(mins, digits = 3), max = round(maxs, digits = 3), K = round(ks, digits = 3))
datatable(poptib %>% arrange(cv))
```



### Parameter dot plots

Coerce to ggs object
```{r cache=FALSE}
mod.gg <- ggs(as.mcmc(topmod), keep_original_order = TRUE)
```

Remind covariate names...
```{r}
names.covars0
```

Covariate types and pretty covariate/population names
```{r}
CovType <- factor(c(rep("Managed flow", times = 6), 
                    rep("Natural flow", times = 1), 
                    rep("Experienced flow", times = 2), 
                    rep("Temperature", times = 4)),
                  levels = c("Managed flow", "Natural flow", "Experienced flow", "Interaction"))

# rename covariates
names.covars.new <- c("Duration of ramp down", 
                      "Timing of ramp down", 
                      "Mgd. winter flow variation", 
                      "Mgd. summer mean flow", 
                      "Mgd. peak flow mag. (0)", 
                      "Mgd. peak flow mag. (1)", 
                      "Nat. peak flow magnitude", 
                      "Exp. flood duration",
                      "Exp. flood duration squared",
                      "Autumn temperature", 
                      "Winter temperature", 
                      "Spring temperature", 
                      "Summer temperature")

# short population names
popshort <- c("THCH", "BLKT", "BLCR", "COCA", "FISH", "FLAT", "LTBC", "LOBC", "NOWL", "PRCE", "SRSC", "SPRG", "UPBC")
```

Set color palette
```{r}
# bls <- hcl.colors(5, "Blues3")
# mycols <- c("darkorange", bls[c(3,1)], "seagreen", "grey50")
mycols <- c("#E69F00", "#56B4E9", "#009E73", "#999999")
#palette_check(col2hcl(mycols), plot = TRUE)
```

#### Global covariate effects
```{r fig.width=5.5, fig.height=6}
# ggs_caterpillar(D = mod.gg, family = "mu.coef", thick_ci = c(0.125, 0.875), thin_ci = c(0.025, 0.975), sort = FALSE) +
#   theme_bw() + 
#   ylab("Environmental driver") + 
#   xlab("Global change in productivity, ln(R/S)") + 
#   aes(color = CovType) +
#   scale_color_manual(values = mycols) +
#   geom_vline(xintercept = 0, linetype = "dashed") + 
#   scale_y_discrete(labels = rev(names.covars.new), limits = rev) +
#   theme(legend.position = "top", legend.title = element_blank(), axis.text = element_text(color = "black"),
#         legend.key.spacing.y = unit(0, "cm"), legend.key.spacing.x = unit(1, "cm"), legend.margin = margin(0,0,0,0), panel.grid = element_blank()) + 
#   guides(color = guide_legend(nrow = 2, byrow = TRUE))
test <- ggs_caterpillar(mod.gg %>% 
                  filter(Parameter %in% grep("mu.coef", unique(mod.gg$Parameter), value = TRUE)) %>%
                  mutate(Parameter = factor(Parameter, levels = c("mu.coef[1]", "mu.coef[2]", "mu.coef[3]", "mu.coef[4]", "mu.coef[5]", "mu.coef[6]", "mu.coef[7]", "mu.coef[8]", "mu.coef[9]", "mu.coef[10]", "mu.coef[11]", "mu.coef[12]", "mu.coef[13]"))), 
                thick_ci = c(0.125, 0.875), thin_ci = c(0.025, 0.975), sort = FALSE)
test +
  theme_bw() + 
  ylab("Environmental driver") + 
  xlab("Global change in productivity, ln(R/S)") + 
  aes(color = CovType) +
  scale_color_manual(values = mycols) + 
  geom_rect(aes(xmin = -Inf, xmax = Inf, ymin = 7.5, ymax = 9.5), fill = "grey80", color = NA) +
  geom_vline(xintercept = 0, linetype = "dashed") + 
  scale_y_discrete(labels = rev(names.covars.new), limits = rev) +
  theme(legend.position = "top", legend.title = element_blank(), axis.text = element_text(color = "black"),
        legend.key.spacing.y = unit(0, "cm"), legend.key.spacing.x = unit(1, "cm"), legend.margin = margin(0,0,0,0), 
        panel.grid = element_blank(), axis.title = element_text(size = 14)) + 
  guides(color = guide_legend(nrow = 2, byrow = TRUE)) +
  geom_point(data = test$data, aes(x = median, y = Parameter), size = 3) +
  geom_errorbarh(data = test$data, aes(xmin = Low, xmax = High), size = 1.5, height = 0) +
  geom_errorbarh(data = test$data, aes(xmin = low, xmax = high), height = 0) +
  geom_point(data = test$data, aes(x = median, y = Parameter), size = 3, shape = 1, color = "black")


# test <- ggs_caterpillar(D = mod.gg, family = "mu.coef", thick_ci = c(0.125, 0.875), thin_ci = c(0.025, 0.975), sort = FALSE)
# test +
#   theme_bw() + 
#   ylab("Environmental driver") + 
#   xlab("Global change in productivity, ln(R/S)") + 
#   aes(color = CovType) +
#   scale_color_manual(values = mycols) + 
#   geom_rect(aes(xmin = -Inf, xmax = Inf, ymin = 8.5, ymax = 10.5), fill = "grey80", color = NA) +
#   geom_vline(xintercept = 0, linetype = "dashed") + 
#   #scale_y_discrete(labels = rev(names.covars.new), limits = rev) +
#   theme(legend.position = "top", legend.title = element_blank(), axis.text = element_text(color = "black"),
#         legend.key.spacing.y = unit(0, "cm"), legend.key.spacing.x = unit(1, "cm"), legend.margin = margin(0,0,0,0), 
#         panel.grid = element_blank(), axis.title = element_text(size = 14)) + 
#   guides(color = guide_legend(nrow = 2, byrow = TRUE)) +
#   geom_point(data = test$data, aes(x = median, y = Parameter), size = 3) +
#   geom_errorbarh(data = test$data, aes(xmin = Low, xmax = High), size = 1.5, height = 0) +
#   geom_errorbarh(data = test$data, aes(xmin = low, xmax = high), height = 0) +
#   geom_point(data = test$data, aes(x = median, y = Parameter), size = 3, shape = 1, color = "black")
```


```{r}
nvalues <- 100
# 1. duration of ramp down
x1 <- seq(from = min(dat1$z_durflood, na.rm = TRUE), to = max(dat1$z_durflood, na.rm = TRUE), length.out = nvalues)
# axes
x.axis <- seq(from = 5, to = 30, by = 5)
x.axis.scaled <- (x.axis - covsummary$mean[1]) / covsummary$sd[1]
# predictions
pred <- matrix(NA, nrow = nrow(Mcmcdat), ncol = nvalues)
for (j in 1:nrow(pred)) { pred[j,] <- Mcmcdat[j,"mu.A"] + Mcmcdat[j,"mu.coef[8]"]*x1 + Mcmcdat[j,"mu.coef[9]"]*(x1^2) }
pred_median <- apply(pred, MARGIN = 2, quantile, prob = 0.50) 
pred_025 <- apply(pred, MARGIN = 2, quantile, prob = 0.025)
pred_125 <- apply(pred, MARGIN = 2, quantile, prob = 0.125)
pred_875 <- apply(pred, MARGIN = 2, quantile, prob = 0.875)
pred_975 <- apply(pred, MARGIN = 2, quantile, prob = 0.975)
# store in tibble
mytib <- tibble(x1 = x1, pred_median = pred_median, pred_025 = pred_025, pred_125 = pred_125, pred_875 = pred_875, pred_975 = pred_975)
# plot
ggplot(mytib, aes(x = x1, y = pred_median)) +
  geom_ribbon(aes(ymin = pred_025, ymax = pred_975), fill = "grey85") +
  geom_ribbon(aes(ymin = pred_125, ymax = pred_875), fill = "grey70") +
  geom_hline(yintercept = param.summary["mu.A",5], linetype = "dashed", color = "grey40") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey40") +
  annotate("text", x = 0.1, y = 0.3, label = "10", color = "grey40", hjust = 0, vjust = 0.5) +
  geom_line(linewidth = 1.2, lineend = "round") +
  coord_cartesian(ylim = c(0.3,2)) +
  # scale_x_continuous(breaks = x.axis.scaled, labels = x.axis) +
  xlab("Duration of ramp down (days)") + ylab("Productivity, ln(R/S)") +
  theme_bw() +
  theme(panel.grid = element_blank(), axis.text = element_text(color = "black"))

```

